### 2016-06-23 appendix.tex
Revise Sec 5 last portion and Appendix

\appendix
\section{Proofs of Theorems}
\subsection{Proof of Theorem~\ref{THM:RP_ETA}} 
\label{appx:proof-rp-eta}
\begin{proof}
We compute $\eta$ by analyzing $\range(\rho_{G,L,K}(\cdot))$.
In the following, when no ambiguity, we use $\rho(T)$ to represent
$\rho_{G,L,K}(T)$. For any sequence $T$, its $\rho(T)$ can
be viewed as interleaving segments and gaps. 
We may view $\rho(T)$ as $l_1,g_1,\ldots, l_{n-1}, g_{n-1}, l_n$, where $l_i$ is a
segment and $g_i$ is a gap. For simplicity, we use $l_i$ and $g_i$ directly as their sizes.
Then the
range of $\rho(T)$ is $\Sigma_{i=1}^{i=n} l_i + \Sigma_{i=1}^{i=n-1} g_i$. 
Since $\rho(T)$ is valid, the following constraints holds: 
(1) $\Sigma_{i=1}^{i=n} l_i \geq K$; (2) $\forall l_i$, $l_i \geq L$;
(3) $\forall g_i$, $g_i \leq G-1$. Based on constraint (1) and (2), 
$n \leq \lceil \frac{K}{L}\rceil$. 
This indicates that $\Sigma_{i=1}^{i=n-1} g_i \leq (\lceil \frac{K}{L}\rceil -1 ) (G-1)$.
If $l_n > L$ and $\Sigma_{i=1}^{i=n} l_i > K$, we can reduce the range of $\rho(T)$
by reducing $l_n$. If $\Sigma_{i=1}^{i=n} l_i - K < l_n - L$ 
then, $\Sigma_{i=1}^{i=n} l_i - K$ can be reduced to $K$. In this case, the maximum range of $\rho(T)$ is 
$\leq K +(\lceil \frac{K}{L}\rceil -1 ) (G-1)$.
Otherwise, we can reduce $l_n$ to be $L$. When $l_n = L$, 
since we wish $\rho(T)$ to be minimum, it indicates $\Sigma_{i=1}^{i=n} l_i \leq K-1$.
Therefore $\Sigma_{i=1}^{i=n} l_i \leq K-1+L$. In this case,
the maximum range of  $\rho(T)$ is $K-1+L +(\lceil \frac{K}{L}\rceil -1 ) (G-1)$.
Taking maximum, the maximal possible $\rho(T)$ for all $T$s is thus $K-1+L +(\lceil \frac{K}{L}\rceil -1 ) (G-1)$. This proves the first half of the theorem.

For the second half of theorem, we prove by construction. Given $G,L,K$, let $\eta^*$
be the optimal value. Then consider the sequence $T$ generated 
by replicate the following pattern: a $L$-segment followed by $G$-gap. The replication
stops when $|T|\geq K$. Apparently $T$ is valid wrt. $G,L,K$.
It is easy to see that the minimum $\range(\rho(T))$ 
is $(\lceil \frac{K}{L}\rceil -1 ) (G-1) + K$. Since $\eta^*$ is optimal,
$\eta^* \geq \range(\rho(T)) = (\lceil \frac{K}{L}\rceil -1 ) (G-1) + K$. Recall $\eta =(\lceil \frac{K}{L}\rceil -1 ) (G-1) + K +L-1$, this implies that $\eta \leq \eta^* + L - 1$. 
\end{proof}
%\subsection{Proof of Theorem~\ref{THM:RP_ETA}}
%\begin{proof}
%Let $T'$ be the \emph{shortest} valid subsequence (wrt. $K,L,G$) 
%of a valid sequence $T$. Let $\eta$ be the upper bound for all $T'$s among 
%all possible valid sequence. It is easy to see that, under such a setting,
%any valid sequence would be captured by one of the partitions in temporal
%replication. This proves the completeness. Now, we compute the minimum value
%of $\eta$ as follows:
%any $T'$ can be viewed as $n$ consecutive segments with sizes $l_1,..,l_n$
%and $n-1$ gaps with sizes $g_1,...,g_{n-1}$. Since $\eta$ is the upper bond among all $T'$s, $\eta$ can be formulated 
%as follows:
%\begin{equation}
%\eta = \max_{n,l_i,g_i} \{ \Sigma_{i=1}^{i=n} l_i + \Sigma_{i=1}^{i=n-1} g_i \}
%\end{equation}
%With the following constraints: (1)$\forall l_i, L \leq l_i \leq K-1$;(2)
%$\forall g_i, 1 \leq g_i \leq G$; (3) $\Sigma_{i=1}^{i=n} l_i \geq K$ and
%(4) $\Sigma_{i=1}^{i=n-1}l_i  \leq K-1$. The constraint (1)(2)(3) due to the 
%validity of $T'$ and the constraint (4) is because of the minimum size of $T'$.
%Observe that, constraints (1)-(4) form a convex polygon and $\eta$ is monotone
%increasing wrt. $n,l_i,g_i$, the maximum value of $\eta$ is thus taken at the boundaries. Further
%observe that $n \in [2, \lceil \frac{K}{L} \rceil]$ and $K \geq 1$, these
%conditions naturally derive
%$\eta = (\lceil \frac{K}{L} \rceil -1)*G+2K -2$.
%%valid pattern $P$, let $T'$ be the subsequence of $P.T$ which conforms to $K,L,G$ 
%%with the smallest length. Note that there could be many qualified $T'$s. 
%%Let the $i^{th}$ local-consecutive segment of $T'$ be $l_i$ and 
%%let the $i^{th}$ gap of $T'$ be $g_i$. Then, the size of $T'$ can 
%%be written as $\Sigma_i (l_i + g_i)$.  Since $T'$ conforms to $K,L,G$, 
%%then $2K \geq \Sigma_i (l_i) \geq K$, $l_i \geq L$, $g_i \leq G$. 
%%It follows: $\Sigma_i(l_i+g_i) \leq (\lceil \frac{K}{L} \rceil -1) *G+2K$. 
%%If every partition is of at least such a size, then $T'$ must be
%%captured by at least one of the partition. Thus, the pattern $P$ would 
%%be valid in that partition. This proves the completeness.
%\end{proof}

>>>>

\appendix
\section{Proofs of Theorems}
%\subsection{Proof of Theorem~\ref{THM:RP_ETA}} 
%\label{appx:proof-rp-eta}
%\begin{proof}
%We compute $\eta$ by analyzing $\range(\rho_{G,L,K}(\cdot))$.
%In the following, when no ambiguity, we use $\rho(T)$ to represent
%$\rho_{G,L,K}(T)$. For any sequence $T$, its $\rho(T)$ can
%be viewed as interleaving segments and gaps. 
%We may view $\rho(T)$ as $l_1,g_1,\ldots, l_{n-1}, g_{n-1}, l_n$, where $l_i$ is a
%segment and $g_i$ is a gap. For simplicity, we use $l_i$ and $g_i$ directly as their sizes.
%Then the
%range of $\rho(T)$ is $\Sigma_{i=1}^{i=n} l_i + \Sigma_{i=1}^{i=n-1} g_i$. 
%Since $\rho(T)$ is valid, the following constraints holds: 
%(1) $\Sigma_{i=1}^{i=n} l_i \geq K$; (2) $\forall l_i$, $l_i \geq L$;
%(3) $\forall g_i$, $g_i \leq G-1$. Based on constraint (1) and (2), 
%$n \leq \lceil \frac{K}{L}\rceil$. 
%This indicates that $\Sigma_{i=1}^{i=n-1} g_i \leq (\lceil \frac{K}{L}\rceil -1 ) (G-1)$.
%If $l_n > L$ and $\Sigma_{i=1}^{i=n} l_i > K$, we can reduce the range of $\rho(T)$
%by reducing $l_n$. If $\Sigma_{i=1}^{i=n} l_i - K < l_n - L$ 
%then, $\Sigma_{i=1}^{i=n} l_i - K$ can be reduced to $K$. In this case, the maximum range of $\rho(T)$ is 
%$\leq K +(\lceil \frac{K}{L}\rceil -1 ) (G-1)$.
%Otherwise, we can reduce $l_n$ to be $L$. When $l_n = L$, 
%since we wish $\rho(T)$ to be minimum, it indicates $\Sigma_{i=1}^{i=n} l_i \leq K-1$.
%Therefore $\Sigma_{i=1}^{i=n} l_i \leq K-1+L$. In this case,
%the maximum range of  $\rho(T)$ is $K-1+L +(\lceil \frac{K}{L}\rceil -1 ) (G-1)$.
%Taking maximum, the maximal possible $\rho(T)$ for all $T$s is thus $K-1+L +(\lceil \frac{K}{L}\rceil -1 ) (G-1)$. This proves the first half of the theorem.
%
%For the second half of theorem, we prove by construction. Given $G,L,K$, let $\eta^*$
%be the optimal value. Then consider the sequence $T$ generated 
%by replicate the following pattern: a $L$-segment followed by $G$-gap. The replication
%stops when $|T|\geq K$. Apparently $T$ is valid wrt. $G,L,K$.
%It is easy to see that the minimum $\range(\rho(T))$ 
%is $(\lceil \frac{K}{L}\rceil -1 ) (G-1) + K$. Since $\eta^*$ is optimal,
%$\eta^* \geq \range(\rho(T)) = (\lceil \frac{K}{L}\rceil -1 ) (G-1) + K$. Recall $\eta =(\lceil \frac{K}{L}\rceil -1 ) (G-1) + K +L-1$, this implies that $\eta \leq \eta^* + L - 1$. 
%\end{proof}
%\subsection{Proof of Theorem~\ref{THM:RP_ETA}}
%\begin{proof}
%Let $T'$ be the \emph{shortest} valid subsequence (wrt. $K,L,G$) 
%of a valid sequence $T$. Let $\eta$ be the upper bound for all $T'$s among 
%all possible valid sequence. It is easy to see that, under such a setting,
%any valid sequence would be captured by one of the partitions in temporal
%replication. This proves the completeness. Now, we compute the minimum value
%of $\eta$ as follows:
%any $T'$ can be viewed as $n$ consecutive segments with sizes $l_1,..,l_n$
%and $n-1$ gaps with sizes $g_1,...,g_{n-1}$. Since $\eta$ is the upper bond among all $T'$s, $\eta$ can be formulated 
%as follows:
%\begin{equation}
%\eta = \max_{n,l_i,g_i} \{ \Sigma_{i=1}^{i=n} l_i + \Sigma_{i=1}^{i=n-1} g_i \}
%\end{equation}
%With the following constraints: (1)$\forall l_i, L \leq l_i \leq K-1$;(2)
%$\forall g_i, 1 \leq g_i \leq G$; (3) $\Sigma_{i=1}^{i=n} l_i \geq K$ and
%(4) $\Sigma_{i=1}^{i=n-1}l_i  \leq K-1$. The constraint (1)(2)(3) due to the 
%validity of $T'$ and the constraint (4) is because of the minimum size of $T'$.
%Observe that, constraints (1)-(4) form a convex polygon and $\eta$ is monotone
%increasing wrt. $n,l_i,g_i$, the maximum value of $\eta$ is thus taken at the boundaries. Further
%observe that $n \in [2, \lceil \frac{K}{L} \rceil]$ and $K \geq 1$, these
%conditions naturally derive
%$\eta = (\lceil \frac{K}{L} \rceil -1)*G+2K -2$.
%%valid pattern $P$, let $T'$ be the subsequence of $P.T$ which conforms to $K,L,G$ 
%%with the smallest length. Note that there could be many qualified $T'$s. 
%%Let the $i^{th}$ local-consecutive segment of $T'$ be $l_i$ and 
%%let the $i^{th}$ gap of $T'$ be $g_i$. Then, the size of $T'$ can 
%%be written as $\Sigma_i (l_i + g_i)$.  Since $T'$ conforms to $K,L,G$, 
%%then $2K \geq \Sigma_i (l_i) \geq K$, $l_i \geq L$, $g_i \leq G$. 
%%It follows: $\Sigma_i(l_i+g_i) \leq (\lceil \frac{K}{L} \rceil -1) *G+2K$. 
%%If every partition is of at least such a size, then $T'$ must be
%%captured by at least one of the partition. Thus, the pattern $P$ would 
%%be valid in that partition. This proves the completeness.
%\end{proof}

### 2016-06-23 sec3_definitions.tex
Revise Sec 5 last portion and Appendix

\section{Definitions}
\label{sec:definition}
Let $\mathbb{O} = \{o_1 ,o_2,...,o_n\}$ be the set of objects and $\mathbb{T} =(1,2,...,m)$ be the discretized temporal dimension. 
A time sequence $T$ is defined as a ordered subset of $\mathbb{T}$. 
Let $T[i]$ be the $i$-th entry of the sequence $T$ and $i$ starts from 1.
We allow the traditional set operators 
such as \emph{membership}, \emph{union}, \emph{intersect},
\emph{difference}, \emph{candinality}, \emph{min},  \emph{max} and  \emph{range} on 
sequences without changing their semantics. 
Since sequences are ordered, we distinguish the concept of \emph{subset}
and \emph{subsequence}. Given two sequence $T_1$ and $T_2$, 
$T_1$ is a \emph{subset} of $T_2$, if $\forall t \in T_1$ implies $t \in T_2$.
$T_1$ is a \emph{subsequence} of $T_2$, if $\exists i \in (0,..,|T_2|), \forall j \in (1,..,|T_1|),  T_1[j]=T_2[i+j]$.
It is notable that a subsequence is always a subset, but not vice versa. We use $T[i:j]$ to denote
the subsequence of $T$ from $i$-th entry to $j$-th entry inclusively.

We say a sequence $T$ is consecutive 
if $\forall i \in (1,...,|T|-1), T[i+1] = T[i] + 1$.  We refer a consecutive
portion of $T$ as a \emph{segment}.
It is obvious that any time sequence $T$ can be decomposed into
segments and we say $T$ is \textit{L-consecutive}~\cite{li2015platoon} 
if the length of every segment is no smaller than $L$.

As illustrated in Figure~\ref{fig:platoon_weakpoint}, patterns adopting the notion of $L$-consecutiveness (e.g., \emph{platoon} and \emph{group}) still suffer from the \emph{loose connection} problem. 
To avoid such an anomaly without losing pattern generality, we introduce a parameter $G$ to control the gaps between
timestamps in a pattern. Formally, a $G$-connected time sequence is defined as follows:

@@

Given a trajectory database discretized into snapshots, we can conduct a clustering method, either disk-based or density-based, to identify groups with spatial proximity. Let $T$ be the set of timestamps in which a group of objects $O$ are clustered. We are ready to define a more general co-movement pattern:
\begin{definition}[General Co-Movement Pattern]
A general co-movement pattern finds a set of objects $O$ satisfying the following five constraints: 1) \textit{closeness:} the objects in $O$ belong to the same cluster in the timestamps of $T$; 2) \textit{significance:} $|O| \geq M$; 3) \textit{duration:} $|T| \geq K$; 4) \textit{consecutiveness:} $T$ is L-consecutive; and 5) \textit{connection:} $T$ is $G$-connected.
\end{definition}
There are four parameters in our general co-movement pattern, including object constraint $M$ and temporal constraints $K,L,G$.  By customizing these parameters, our pattern can 
express other patterns proposed in previous literature, as illustrated in Table~\ref{tbl:patterns}. 
In particular, by setting $G=|\mathbb{T}|$, we achieve the \emph{platoon} pattern. By setting $G=|\mathbb{T}|,L=1$, we achieve the \emph{swarm} pattern. By setting $G=|\mathbb{T}|$, $M=2$, $K=1$, we gain the \emph{group} pattern. Finally by setting $G=1$, we achieve the \emph{convoy} and \emph{flock} patterns. 
In addition to the flexibility of representing other existing patterns, our GCMP is able to avoid the \emph{loose connection} anomaly by tuning the parameter $G$. 
It is notable that GCMP cannot be modeled by existing patterns. 
\begin{table}
\centering
\begin{tabular}{|l|c|c|c|c|c|}
\hline 
Pattern & $M$ & $K$ & $L$ & $G$ & Clustering\\ 
\hline
Group & $2$ & $1$ & $2$ & $|\mathbb{T}|$ & Disk-based\\
\hline
Flock & $\cdot$ & $\cdot$ & $K$ & $1$ & Disk-based \\
\hline 
Convoy & $\cdot$ & $\cdot$ & $K$ & $1$ & Density-based\\ 
\hline 
Swarm & $\cdot$ & $\cdot$ & $1$ & $|\mathbb{T}|$ & Density-based \\ 
\hline 
Platoon & $\cdot$ & $\cdot$ & $\cdot$ & $|\mathbb{T}|$ & Density-based\\ 
\hline 
\end{tabular} 
\caption{Expressing other patterns using GCMP. $\cdot$ indicates a user specified value. $M$ represents the 
object \emph{size} constraint. $K$ represents the \emph{duration} constraint. $L$ represents the \emph{consecutiveness} constraint. $G$ represents the \emph{connection} constraint.}
\label{tbl:patterns}
\end{table}

It is also observable that the number of patterns in GCMP could be exponential under some parameter settings (i.e., 
when expressing \emph{swarm}). In particular, given a parameter $M$, if a pattern $P$ is valid, then any subset of $P$ with 
size $M$ is also a valid pattern. This results in additional $\Sigma_{M\geq i \geq |P.O|} {|P.O| \choose i}$ patterns,
which is clearly overwhelming and redundant. For all these patterns, output $P$ is sufficient. Therefore, we define the \emph{Closed General Co-Movement Pattern} as follows:

@@

For example, let $M=2,K=2,,L=1,G=1$. In Figure~\ref{fig:related_work},
the pattern $P_1 = \{o_3,o_4:1,2,3\}$ is not a closed pattern. This is because $P_2=\{o_3,o_4,o_5:2,3\}$ is a closed pattern since $P_2.O \supset P_1.O$. The closed pattern avoids outputting duplicate information, thus making the result patterns more compact.

Our definition of GCMP is independent of the clustering method. Users can apply different clustering methods to facilitate different application needs. 
We currently expose both disc-region based clustering and DBSCAN as options to the users.

In summary, the goal of this paper is to present a parallel solution for discovering closed GCMP from large-scale trajectory datasets.

Before we move on to the algorithmic part, we list the notations that are used in the following sections.

\begin{table}[h]
\centering
\begin{tabular}{|c|l|} 
\hline
Symbols & Meanings \\
\hline
$S_t$ & snapshot of objects at time $t$ \\
\hline
$M$ & object size constraint \\
\hline 
$K$ & duration constraint\\
\hline
$L$ & consecutiveness constraint\\
\hline
$G$ & connection constraint \\
\hline
$P=(O:T)$ & pattern with object set $O$, time sequence $T$\\
\hline
$\eta$ & replication factor in TRM\\
\hline
$C_t(o)$ & the cluster of object $o$ at time $t$ \\
\hline 
$S_t$ & the set of clusters at time $t$\\
\hline 
$\lambda_i$ & the partition with snapshots $S_t,..,S_{t+\eta-1}$ \\
\hline
$Sr_i $ &  the star of object $i$ \\
\hline 
\end{tabular} 
\caption{Symbols and notions used}
\end{table}

>>>>

\section{Definitions}
\label{sec:definition}
Let $\mathbb{O} = \{o_1 ,o_2,...,o_n\}$ be the set of objects and $\mathbb{T} =(1,2,...,N)$ be the discretized temporal dimension. A time sequence $T$ is defined as a ordered subset of $\mathbb{T}$. Given two time sequences $T_1$ and $T_2$, we define a bunch of commonly-used operators in this paper in Table~\ref{tbl:operators}.

\begin{table}[h] \scriptsize
\centering
\begin{tabular}{|c|l|}
\hline 
\textbf{Operator} & \textbf{Definition} \\ 
\hline
$T[i]$ & the $i$-th element in the sequence $T$ \\ 
\hline
$|T|$ & the number of elements in $T$\\
\hline
$\max(T)$ & the maximum element in $T$\\
\hline
$\min(T)$ & the minimum element in $T$\\
\hline
$\range(T)$ & the range of $T$, i.e., $\max(T) - \min(T) +1$\\ 
\hline 
$T[i:j]$ & subsequence of $T$ from $T[i]$ to $T[j]$ (inclusive) \\ 
\hline
$T_1\subseteq T_2$ &  $\forall T_1[x]\in T_1$, we have $T_1[x]\in T_2$. \\\hline
$T_3=T_1\cup T_2$ & $\forall T_3[x]\in T_3$, we have $T_3[x]\in T_1$ or $T_3[x] \in T_2$\\ 
\hline
$T_3=T_1\cap T_2$ & $\forall T_3[x]\in T_3$, we have $T_3[x]\in T_1$ and $T_3[x] \in T_2$\\ 
\hline
\end{tabular}
\caption{Operators on time sequence.} \label{tbl:operators}
\end{table}

We say a sequence $T$ is consecutive 
if $\forall i \in (1,...,|T|-1), T[i+1] = T[i] + 1$.  We refer each consecutive subsequence of $T$ as a \emph{segment}.
It is obvious that any time sequence $T$ can be decomposed into
segments and we say $T$ is \textit{L-consecutive}~\cite{li2015platoon} 
if the length of every segment is no smaller than $L$. As illustrated in Figure~\ref{fig:platoon_weakpoint}, patterns adopting the notion of $L$-consecutiveness (e.g., \emph{platoon} and \emph{group}) still suffer from the \emph{loose connection} problem. 
To avoid such an anomaly without losing pattern generality, we introduce a parameter $G$ to control the gaps between
timestamps in a pattern. Formally, a $G$-connected time sequence is defined as follows:

@@

Given a trajectory database discretized into snapshots, we can conduct a clustering method, either disk-based or density-based, to identify groups with spatial proximity. Let $T$ be the set of timestamps in which a group of objects $O$ are clustered. We are ready to define a more general co-movement pattern:
\begin{definition}[General Co-Movement Pattern]
A general co-movement pattern finds a set of objects $O$ satisfying the following five constraints: (1) \textit{closeness:} the objects in $O$ belong to the same cluster in the timestamps of $T$; (2) \textit{significance:} $|O| \geq M$; (3) \textit{duration:} $|T| \geq K$; (4) \textit{consecutiveness:} $T$ is L-consecutive; and (5) \textit{connection:} $T$ is $G$-connected.
\end{definition}
There are four parameters in our general co-movement pattern, including object constraint $M$ and temporal constraints $K,L,G$.  By customizing these parameters, our pattern can 
express other patterns proposed in previous literature, as illustrated in Table~\ref{tbl:patterns}. 
In particular, by setting $G=|\mathbb{T}|$, we achieve the \emph{platoon} pattern. By setting $G=|\mathbb{T}|,L=1$, we achieve the \emph{swarm} pattern. By setting $G=|\mathbb{T}|$, $M=2$, $K=1$, we gain the \emph{group} pattern. Finally by setting $G=1$, we achieve the \emph{convoy} and \emph{flock} patterns. 
In addition to the flexibility of representing other existing patterns, our GCMP is able to avoid the \emph{loose connection} anomaly by tuning the parameter $G$. 
It is notable that GCMP cannot be modeled by existing patterns. 
\begin{table}[h]
\centering
\begin{tabular}{|l|c|c|c|c|c|}
\hline 
\textbf{Pattern} & $M$ & $K$ & $L$ & $G$ & \textbf{Clustering} \\ 
\hline
Group & $2$ & $1$ & $2$ & $|\mathbb{T}|$ & Disk-based\\
\hline
Flock & $\cdot$ & $\cdot$ & $K$ & $1$ & Disk-based \\
\hline 
Convoy & $\cdot$ & $\cdot$ & $K$ & $1$ & Density-based\\ 
\hline 
Swarm & $\cdot$ & $\cdot$ & $1$ & $|\mathbb{T}|$ & Density-based \\ 
\hline 
Platoon & $\cdot$ & $\cdot$ & $\cdot$ & $|\mathbb{T}|$ & Density-based\\ 
\hline 
\end{tabular} 
\caption{Expressing other patterns using GCMP. $\cdot$ indicates a user specified value. $M$ represents the 
object \emph{size} constraint. $K$ represents the \emph{duration} constraint. $L$ represents the \emph{consecutiveness} constraint. $G$ represents the \emph{connection} constraint.}
\label{tbl:patterns}
\end{table}
\eat{ 
It is also observable that the number of patterns in GCMP could be exponential under some parameter settings (i.e., 
when expressing \emph{swarm}). In particular, given a parameter $M$, if a pattern $P$ is valid, then any subset of $P$ with 
size $M$ is also a valid pattern. This results in additional $\Sigma_{M\geq i \geq |P.O|} {|P.O| \choose i}$ patterns,
which is clearly overwhelming and redundant. For all these patterns, output $P$ is sufficient. Therefore, we define the \emph{Closed General Co-Movement Pattern} as follows:

@@

For example, let $M=2,K=2,,L=1,G=1$. In Figure~\ref{fig:related_work},
the pattern $P_1 = \{o_3,o_4:1,2,3\}$ is not a closed pattern. This is because $P_2=\{o_3,o_4,o_5:2,3\}$ is a closed pattern since $P_2.O \supset P_1.O$. The closed pattern avoids outputting duplicate information, thus making the result patterns more compact. 
}

Our definition of GCMP is independent of the clustering method. Users can apply different clustering methods to facilitate different application needs. 
We currently expose both disc-region based clustering and DBSCAN as options to the users. In summary, the goal of this paper is to present a parallel solution for discovering all the valid GCMP from large-scale trajectory datasets. Before we move on to the algorithmic part, we list the notations that are used in the following sections.

\begin{table}[h]\scriptsize
\centering
\begin{tabular}{|c|l|} 
\hline
Symbol & Meaning \\
\hline
$S_t$ & snapshot of objects at time $t$ \\
\hline
$M$ & object size constraint \\
\hline 
$K$ & duration constraint\\
\hline
$L$ & consecutiveness constraint\\
\hline
$G$ & connection constraint \\
\hline
$P=\langle O:T \rangle$ & pattern with object set $O$, time sequence $T$\\
\hline
$\eta$ & replication factor in the TRPM framework\\
\hline
$C_t(o)$ & the cluster of object $o$ at time $t$ \\
\hline 
$S_t$ & the set of clusters at time $t$\\
\hline 
$\lambda_t$ & the partition with snapshots $S_t,..,S_{t+\eta-1}$ \\
\hline
$Sr_i $ &  the star partition for object $i$ \\
\hline 
\end{tabular} 
\caption{Symbols and notions used}
\end{table}
